The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-05-30 article.tex
Ready for feedback

% Use multi-line cell
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

@@

The PBD model has five biological parameters, depicted in table \ref{table:parameters}, 
which we explore in a factorial fashion, excluding some combinations.
% HIERO
We simulate a PBD process for those combinations in which the 
95\% quantile has less than 1250 extant good species. The quantile is
calculated with a recently added function to the PBD package,
inspired on equation 6 of \cite{etienne2014}. This calculation
assumes $b = b_g = b_i$, we used $b = \max(b_g, b_i)$.
We use 1250 good species as a threshold, to prevent overly taxon-poor and taxon-rich phylogenies respectively.
The parameter values chosen are based on the parameter sets used by 
\cite{etienne2014}, as these parameters were shown to result in reasonably
sized phylogenies and using the same set allows us to compare results. 
For the speciation initiation rates of good and incipient species, $b_g$ and $b_i$ 
respectively, we use $0.3$ and $0.5$ speciation initiation events per good/incipient species per time unit.
The speciation completion rates we use are $0.1$, $0.3$, $1.0$ and $10^9$ speciation completion
events per (incipient species) species per time unit. We use $10^9 \approx \infty$
to mimic the BD model, because the PBD model reduces to the BD model for $\lambda = \infty$.
This allows us to measure the baseline error, 
which is the difference between inferred tree and true species tree that arises purely due to noise 
because the generating model and the model used in inference are identical in this case.
The extinction rates of good and incipient species, $\mu_g$ and $\mu_i$ respectively, 
that we use are $0.0$, $0.1$ and $0.2$ 
extinction events per good/incipient species per time unit.

>>>>

@@

The PBD model has five biological parameters, depicted in table \ref{table:parameters}, 
which we explore in a factorial fashion, excluding some combinations.
We simulate a PBD process for those combinations in which the 
95\% quantile of the expected number of good species is less than 1250.
The quantile is
calculated with a recently added function to the PBD package,
based on equation 6 of \cite{etienne2014}. This calculation
assumes $b = b_g = b_i$, we used $b = \max(b_g, b_i)$.
We use 1250 good species as a threshold, to prevent overly taxon-poor and taxon-rich phylogenies respectively.
The parameter values chosen are based on the parameter sets used by 
\cite{etienne2014}, as these parameters were shown to result in reasonably
sized phylogenies and using the same set allows us to compare results. 
For the speciation initiation rates of good and incipient species, $b_g$ and $b_i$ 
respectively, we use $0.3$ and $0.5$ speciation initiation events per good/incipient species per time unit.
The speciation completion rates we use are $0.1$, $0.3$, $1.0$ and $10^9$ speciation completion
events per (incipient species) species per time unit. We use $10^9 \approx \infty$
to mimic the BD model, because the PBD model reduces to the BD model for $\lambda = \infty$.
This allows us to measure the baseline error, 
which is the difference between inferred tree and true species tree that arises purely due to noise 
because the generating model and the model used in inference are identical in this case.
The extinction rates of good and incipient species, $\mu_g$ and $\mu_i$ respectively, 
that we use are $0.0$, $0.1$ and $0.2$ 
extinction events per good/incipient species per time unit.
